P4IRS: An Intermediate Representation and Compiler for Parallel and Performance-Portable Particle Simulations

### 2024-07-03 sage_latex_template/manuscript.tex
Small fixes for SAGE template
Signed-off-by: Rafael Ravedutti <rafael.r.ravedutti@fau.de>

\begin{lstlisting}[language=Python,
		   label={lst:euler},
		   caption={Euler integrator description in P4IRS.}]
def euler(i):
    linear_velocity[i] += dt * force[i] / mass[i]
    position[i] += dt * linear_velocity[i]
\end{lstlisting}

@@

# Particle properties
psim.add_position('position')
psim.add_property('mass', pairs.real(), 1.0)
psim.add_property('linear_velocity', pairs.vector())
psim.add_property('force', pairs.vector(), volatile=True)

@@

# Initial state
psim.read_particle_data(
	"data/copper_fcc_lattice.input",
	['type', 'mass', 'position', 'linear_velocity', 'flags'],
	pairs.point_mass())

# Optimization settings
psim.reneighbor_every(20)
psim.compute_half()
psim.build_neighbor_lists(cutoff_radius + skin)
psim.vtk_output(f"output/md_{target}", every=20)

@@

\begin{lstlisting}[language=Python,
		   label={lst:contactprops1},
		   caption={Setup example for contact properties.}]
psim.add_contact_property('is_sticking', pairs.int32(), 0)
psim.add_contact_property('tangential_spring_displacement', pairs.vector(), [0.0, 0.0, 0.0])
psim.add_contact_property('impact_velocity_magnitude', pairs.real(), 0.0)
\end{lstlisting}

@@

\begin{lstlisting}[language=Python,
		   label={lst:contactprops2},
		   caption={Usage example for contact properties.}]
def linear_spring_dashpot(i, j):
    # ...
    tan_spring_disp = tangential_spring_displacement[i, j]
    impact_vel_magnitude = impact_velocity_magnitude[i, j]
    impact_magnitude = select(impact_vel_magnitude > 0.0, impact_vel_magnitude, length(rel_vel))
    # ...
    tangential_spring_displacement[i, j] = new_tan_spring_disp
    impact_velocity_magnitude[i, j] = impact_magnitude
    is_sticking[i, j] = n_sticking
\end{lstlisting}

@@

\begin{lstlisting}[language=C++,
		   label={lst:pairsruntime},
	   	   caption={P4IRS runtime routine example for writing VTK data into a file.}]
void vtk_write_data(PairsRuntime *ps, const char *filename, int start, int end, int timestep) {
    std::string output_filename(filename);
    auto position = ps->getAsVectorProperty(ps->getPropertyByName("position"));
    // ...
    filename_oss << filename << "_";
    if(ps->getDomainPartitioner()->getWorldSize() > 1) {
        filename_oss << ps->getDomainPartitioner()->getRank() << "_";
    }
    // ...
    filename_oss << timestep << ".vtk";
    std::ofstream out_file(filename_oss.str());
    // ...
    ps->copyPropertyToHost(position);
    for(int i = start; i < end; i++) {
        out_file << position(i, 0) << " ";
        out_file << position(i, 1) << " ";
        out_file << position(i, 2) << "\n";
    }
    // ...
}
\end{lstlisting}

>>>>

\begin{lstlisting}[language=Python,
		   label={lst:euler},
		   caption={Euler integrator description in P4IRS.}]
def euler(i):
    velocity[i] += dt * force[i] / mass[i]
    position[i] += dt * velocity[i]
\end{lstlisting}

@@

# Particle properties
psim.add_position('position')
psim.add_property('mass', pairs.real(), 1.0)
psim.add_property('velocity', pairs.vector())
psim.add_property('force', pairs.vector(), volatile=True)

@@

# Initial state
psim.read_particle_data(
  "data/copper_fcc_lattice.input",
  ['type', 'mass', 'position', 'velocity'],
  pairs.point_mass())

# Optimization settings
psim.reneighbor_every(20)
psim.compute_half()
psim.build_neighbor_lists(cutoff_radius + skin)
psim.vtk_output("output/md", every=20)

@@

\begin{lstlisting}[language=Python,
		   label={lst:contactprops1},
		   caption={Contact properties setup example.}]
psim.add_contact_property(
  'is_sticking', pairs.int32(), 0)
psim.add_contact_property(
  't_spring_disp', pairs.vector(), [0.0, 0.0, 0.0])
psim.add_contact_property(
  'impact_velocity', pairs.real(), 0.0)
\end{lstlisting}

@@

\begin{lstlisting}[language=Python,
		   label={lst:contactprops2},
		   caption={Contact properties usage example.}]
def linear_spring_dashpot(i, j):
    # ...
    t_disp = t_spring_disp[i, j]
    impact_vel = impact_velocity[i, j]
    impact_magnitude = select(impact_vel > 0.0, impact_vel, length(rel_vel))
    # ...
    t_spring_disp[i, j] = new_t_disp
    impact_velocity[i, j] = impact_magnitude
    is_sticking[i, j] = n_sticking
\end{lstlisting}

@@

\begin{lstlisting}[language=C++,
		   label={lst:pairsruntime},
	   	   caption={P4IRS runtime routine example for writing VTK data into a file.}]
void vtk_write_data(
  PairsRuntime *ps, const char *filename,
  int start, int end, int timestep) {

  std::string output_filename(filename);
  auto position = ps->getAsVectorProperty(
    ps->getPropertyByName("position"));
  auto dom_part = ps->getDomainPartitioner();
  // ...
  filename_oss << filename << "_";
  if(dom_part->getWorldSize() > 1) {
    filename_oss << dom_part->getRank() << "_";
  }
  // ...
  filename_oss << timestep << ".vtk";
  std::ofstream out_file(filename_oss.str());
  // ...
  ps->copyPropertyToHost(position);
  for(int i = start; i < end; i++) {
    out_file << position(i, 0) << " ";
    out_file << position(i, 1) << " ";
    out_file << position(i, 2) << "\n";
  }
  // ...
}
\end{lstlisting}
